Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-19 ms.qmd
Ditched insets. to hard to control labelling

p <- map1_current / (zoom_plots[[1]] | zoom_plots[[2]] | zoom_plots[[3]])

>>>>

# Make a multipanel plot. Make teh world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork

p <- (zoom_plots[[1]] | plot_spacer() | zoom_plots[[2]]) / map1_current  / (plot_spacer() | plot_spacer() |zoom_plots[[3]]) + plot_layout(heights  = c(1, 2.5, 1)) + plot_annotation(tag_levels = "A", tag_suffix = ")")

p
